---
title: "acadcites: Academia Citation Advantage Analysis"
author: "C. Vogel"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{acadcites: Academia Citation Advantage Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The `acadcites` package contains the code and data used by Niyazov, et. al., 
"Open Access Meets Discoverability: Citations to Articles Posted to Academia.edu."

## Importing the data

To import the combined article and journal data, use the function `importData`. 
This will read in two raw datasets: 

1. One with information about papers in the on- and off-Academia sets, including 
   - citation counts from Google Scholar
   - an indicator of whether it appeared to be available for free online from a non-Academia source
   - the ISSN of its journal
   - the impact factor of its journal
2. One with information about journals from the Australian Research Council, including
   - ISSN (many journal have multiple ISSNs)
   - Fields of Research, as classified by the ANZSRC.

Calling `importData()` will import these raw files, clean them, and merge them
on ISSN. All analyses in the paper are based off this combined dataset.

```{r}
library('acadcites')
cites <- importData()
```

## Replicating tables from the article
The `makeTable` function can be used to reproduce any table in the article. `maketable` is called with two arguments: a table number and a dataframe with the articles/journals dataset (as would be returned from `importData()`).

For example to reproduce Table 12 from the article:

```{r}
makeTable(10, cites)
```


## Replicating tables from the article
The `makeFigure` function reproduces figures from the article. Like `makeTable`, 
it takes a figure number and a citations data frame.

```{r}
makeFigure(1, cites)
```

